\subsection*{Fall}
\subsubsection*{Week1}
Wrote biography and printed my resume to bring to class. Chose and submitted my top ten projects and two that I did not want.
\subsubsection*{Week2}
Got project group assignment. Collaborated with team via email to write/agree upon an introduction email for the client. Emailed client with introduction email. Got response email from client asking about availability. Collaborated with group via email to see when the best day and time was to meet. Client chose Fridays at 2pm out of the options we gave them.
\subsubsection*{Week3}
Worked on learning LeTeX. Worked on and finished Problem statement rough draft. Texted with group to figure out times that would work to meet with TA. Responded to TA's email with our availability. TA responded to our email letting us know he will have to get back to us because our group couldn't do any of his timeslots. TA emailed back saying that Friday at 3pm would work so we set that as our meeting time. Client emailed us saying that he had a meeting come up at 2pm on Fridays and it conflicts with our meeting. He asked if we could move our meeting until 2:30pm instead. I emailed the client letting him know it was okay. I emailed the TA to let him know that we may be late to his meetings because our client moved our meeting. TA explored other time options with us. I emailed the client to see if this change in meeting time would be every week, he said yes if that works for us and I said it would. I emailed the client to ask how long his meetings would last and he said no more than thirty minutes. I emailed the TA to let him know that this change would be every week and that we can keep the 3pm appointment with him but that we may be late. The TA was not crazy about this but we kept the 3pm meeting time for this week on Friday but that he would check with another group to see if we could switch to the 3:20pm time slot instead. Met with client for the first time. Met with TA for the first time.
\subsubsection*{Week4}
Texted with group about what research we found. No one had found anything about percent success of projects similar to ours. Emailed Professor Smart to let him know about our research progress. Found a research article that is very similar to what we are trying to do and has a percent accuracy of their method. Worked on Problem Statement ang got it turned in. Emailed Professor Smart with all of the research links that we found and let him know that we found one with information about percent accuracy. Met with Professor Smart.
\subsubsection*{Week5}
Started thinking about the requirements rough draft. Finished requirements rough draft. Met with client. Met with Andrew.
\subsubsection*{Week6}
Started working on requirements final draft based on the meeting from last week. Finished requirements document. Planning on reviewing it with client tomorrow. Client did not show up to meeting. Met with Andrew.
\subsubsection*{Week7}
Since Bill did not show up last week we struggled to do work this week. Split up project for tech review. Veterans day: No meetings.
\subsubsection*{Week8}
Worked on Tech Review Rough Draft. Turned in Tech. Review Rough Draft. Met with Bill. Met with Andrew.
\subsubsection*{Week9}
Had stomach flu. Tech Review due on Tuesday but I did not finish because my part got changed to the training module and I did not know how that works. Also Andrew is going to Kevin to see if we are even going to use a training module. Thanksgiving Weekend: no meetings. 
\subsubsection*{Week10}
Waiting to hear back about what to do about tech document and design document. Asked Kevin about issue to make sure it was being handled, he referred me to Andrew. Emailed Andrew about issue and he informed me that there had been a misunderstanding. Went to Webex meeting with Anderew. Went to help session and talked with Claude about final and design doc. Andrew came to Friday meeting with us and Bill.

\subsection*{Winter}
\subsubsection*{Week1}
Talked about what we accomplished over the break, we had finished the design document, my tech review and had begun the image processing. Discussed the next steps we needed to take which was starting research for the model, getting the camera and setting up meeting times with Bill and Andrew.
\subsubsection*{Week2}
Stuck, did research on model. Everything seemed extremely complicated and I did not understand anything really. Not too much happened this week.
\subsubsection*{Week3}
Met with Bill, finally got info about how to do the model. Bill said to use scikit-learn for the model so I looked into that library and how it works.
\subsubsection*{Week4}
I began to code the linear regression using what I learned about the libbrary but the code was buggy. Worked on debugging. Bill canceled meeting because he was sick.
\subsubsection*{Week5}
I fixed the buggy code and worked on the program that calculated the absolute error and I pretty much finished it. Met with Bill, he went over things about the camera and image processing as well as how a linear regression works.
\subsubsection*{Week6}
I worked on the midterm progress report paper and wrote my section. I worked on the midterm progress report video by making my slides and recorded presentation. I worked on the poster and added info on the model.
\subsubsection*{Week7}
Refined my linear regression code and it ran nicely. Waiting on data from the camera to create the real model. We mutually canceled the meeting with Bill this week because not too many new things had happened since the past week we focused on the midterm reports and the poster.
\subsubsection*{Week8}
Did some research about how people typically set up and test linear regression models. Found out that finding the R squared value instead of the absolute error is a better measure of how well the regression is predicting values.
\subsubsection*{Week9}
Decided to go with the R squared method of determining accuracy. Successfully implemented R squared method. Attended poster extra credit session, made critiques on other groups poster and the other group critiqued our poster. Kirsten contacted us about using our porter on the last day of class so we made some changes to the poster with her help.
\subsubsection*{Week10}
Met for the last day of class. Went over posters and how they should look. The group met to take pictures with the camera under different scenarios to get data. We later found out that all the data was bad because the calibration issue had returned.
\subsection*{Spring}
\subsubsection*{Week1}
Went to the first class. Worked on the poster a bit.
\subsubsection*{Week2}
Went to class, did in class activity. I finished the poster and I let the group know to review it. 
\subsubsection*{Week3}
Met with Bill this week and asked him if it was okay to make changes to our documents and he agreed. He also told us that he would have a graduate student try and take some data for us. Bill also told me that instead of using the R squared value to evaluate the model to use sum of squared error and leave one out cross validation. I also asked him what another model would be that I could try and he said a gaussian model. The graduate student reached out to me to find out how we had been collecting the data and I told her.
\subsubsection*{Week4}
The graduate student sent the data to me and I sent it to Claude for image processing. Claude informed me that the data was bad and that it wouldn't work. We also ended up making some small changes to the poster to refine it and put the finishing touches on it. We took the team picture and added that to the poster as well. We then submitted it for printing. I also worked with Bill to understand how to create a gaussian model and how to understand sum of squared error and leave one out cross validation. He wrote some sample code for me and I used that to make changes to code I had already written. I also finished and turned in my WIRED article.
\subsubsection*{Week5}
We met with Andrew and talked to him about the problems with the data the graduate student had taken. We also talked with him about the new model code I had created and he gave me some suggestions as to how to clean it up and make it more professional. Also, the library that Bill wanted me to use for the gaussian regression is outdated so it produces a ton of warnings. I asked Andrew if he knew how to suppress them since Bill insisted I use that library and Andrew did not know. 
\subsubsection*{Week6}
Made finishing touches to the code because the code freeze was coming up as well as expo. 
\subsubsection*{Week7}
Prepared for expo and went to expo. Expo went well even though there were too many people to run our code properly. We ended up just leaving the thermal camera on so that people could see themselves and then we explained how the code worked. Having the thermal camera on drew a lot of attention to our project and it was fun getting to talk to people. 
\subsubsection*{Week8}
Began to work on the report for Bill that gave details about how our code worked. We also began to work on the final report for the class.  
\subsubsection*{Week9}
We finished the final report for Bill and sent that to him. We  also began to work on the final presentation and continued to work on the final report.
\subsubsection*{Week10}
We all finished creating and recording our slides for the final presentation and we turned that in. We also continued to work on the final report. 