\subsection*{Fall}
	\subsubsection*{Week1}
		Finished picking my projects.
	\subsubsection*{Week2}
		 I met with my group mates this week and exchanged contact information. We decided on a time to meet with our client, however our meeting time will be after the problem statement is due, so we may need to talk to our professors about this.
	\subsubsection*{Week3}
		We met with our client and TA this week. After listening to the client and telling the TA about our meeting he voiced his concerns that this project may have too many components for us to do and it could potentially be too difficult for us to do. I worked and finished my rough draft problem statement after meeting with the client to add more details to my initial draft.
	\subsubsection*{Week4}
		Met with the client to talk about our concerns about the project. The project was changed to something more research oriented so a high accuracy rating was not absolutely required. OpenVL was suggested for image handling which was also one of our concerns. We still have no camera, and still have no idea where the data is coming from.
	\subsubsection*{Week5}
		We now have more guidance and more of an idea as to what to expect for the future of the project. We now have a better idea as to what is going on and how we will be doing the analysis. However we still do not have a camera and are still unsure about where the data will be coming from
	\subsubsection*{Week6}
		We had trouble finishing the requirements document as it was still unclear to the group what the final product will be. The client did not show up for the meeting, so we couldn't double check during the meeting about the requirements. We have sent an email, and are currently waiting for a response.
	\subsubsection*{Week7}
		Not a lot happened this week. No meeting this week because of the holiday on Friday. All that has happened this week is that I looked at the tech review assignment. 
	\subsubsection*{Week8}
		The requirements for the project changed again, so we had to change some of our tech review document to fit these changes. This also meant that we would have to go back and change our requirements document as well.
	\subsubsection*{Week9}
		It's Thanksgiving break, nothing got done.
	\subsubsection*{Week10}
		This week we had trouble getting the design document finished as we could not complete a portion of it. We could not complete it because we had absolutely no idea what was going on with that part. We are allowed to take an incomplete, but I would prefer if we didn't. During this weeks meeting we have our TA attend with us to help us clarify what was actually asked of us. After that meeting we continued to talk with the TA to make what was discussed in the previous meeting more clear. It was pretty helpful overall and it gave us a better idea on what was being asked, and how to fill out the tech review.
\subsection*{Winter}
	\subsubsection*{Week1}
		Nothing much happened this week. This week was mostly getting things together and preparing to create the project. We have a camera, some images and csv files so we are ready to start on the project. We also need to schedule a time where we can meet with Bill and Andrew.
	\subsubsection*{Week2}
		We are slowly working on the project by creating the image processing piece by piece. Claude created the bulk of the program which analyzes the pixels in the images. I created something that creates a histogram out of the csv file, as well as a short program that detects the type of file. The plan is to put all these pieces together to run on both csv and tiff files.
	\subsubsection*{Week3}
		We have the image analysis mostly complete. I created a fake data generator for any portion in the future that needs data. I have also created a reader to go with that data to make it easy to use in python. For the evaluation portion I have decided to look into something called Receiver operating characteristic. This is something that can minimize false positives, so it might also be able to minimize false negatives.
	\subsubsection*{Week4}
		Not much progress on the project was made this week. This week most mostly a lot of planning on what we need to do, and what we needed from the mechanical team. We made some progress on the evaluation portion of the project, and found the a receiver operating characteristic curve would be helpful in evaluating the model.

		We also worked with the camera a little bit. We found that the temperatures that it was producing seemed to be very off, so we need some sort of constant temperature to let the camera have something to compare to.
	\subsubsection*{Week5}
		This week we were mostly working with the camera to see if we could fix the issue with the recorded temperature being too high. We tried multiple different reference temperature, and all of the failed to work. We however found that there was a folder supposed to be used for calibration, and found that when we used that folder the camera was only off my a couple of degrees. We plan on taking more pictures to homely have the camera calibrate correctly.
	\subsubsection*{Week6}
		This week was mostly dedicated to working on the progress report. Claude and I recorded our parts together. Sill not very much progress with the Camera.
	\subsubsection*{Week7}
		Not much was done this week besides testing the camera with the coffee. We were testing if the camera was adjusting to the hottest thing in the room, and the results of the test was that it does adjust. This makes calibrating the camera difficult, as it can only detect things in the range of temperature around the hottest thing it detects.
	\subsubsection*{Week8}
		This week was super busy for me, so not much got accomplished this week. Claude and I met with Chris' to look at his code again and to see how it works.
	\subsubsection*{Week9}
		This week we met with Chris again to go over his code. He wrote his code assuming that we have a Linux machine, so our task is to get one to take data with his code. I am going to try and get a Linux installed on my laptop so we can finally collect data with the camera. Chris' code seems to have better calibration than the window version, so we are more comfortable taking images with it.
	\subsubsection*{Week10}
		We were finally able to gather some data from the camera. To do this we used Chris' code to grab some frames from the camera while it took some video. To do this we needed a linux computer, so I installed Ubuntu on my laptop to have a computer that could use the code. I also wanted to start piecing all the piece of our project together so I can start working on the production mode, and the user interface. However I am still missing the model code so I can't create it yet. I looked at the requirements for the report and the presentation. I plan on working on the report this weekend, and the presentation on Tuesday.
\subsection*{Spring}
	\subsubsection*{Week1}
		Nothing really happened this week. Our group just discussed times we could meet and what we need to accomplish before expo.
	\subsubsection*{Week2}
		We mostly worked on the poster this week. We moved some things around and also wrote out some more stuff to put on the poster. I also did some more testing for the model portion of this project. It seems like the library that we were using just does a Least Squares Regression line. I wrote a small script that does that, so we don't have to import the library in the future if we are to give this project to someone else to work on.
	\subsubsection*{Week3}
		Nothing really happened this week. The only thing that is important was during the meeting with Bill he said that there is a graduate student that is going to help us collect data. This would help greatly in creating the model in the future.
	\subsubsection*{Week4}
		We were able to finish the poster. We decided to put a picture of the mechanical teams rig on the poster as it gives some context as to what we are doing. We also decided to leave the model as is as it works, but it is just highly dependent on data. Bill has also given us some code to use, but a lot of the function he uses inside the library are outdated and throws a lot of errors.
	\subsubsection*{Week5}
		We talked with Andrew about normalizing the data to try and get better results with the image processing. It is something we can try later, but I feel like that will throw errors in the future because if there is no person in the background, and it gets normalized it would detect a person begin there.

		I also worked on the production mode a little bit this week. I tweaked the camera code a little bit so it takes more pictures. I need to look at the image processing code more thoroughly as I don't think I am getting the correct outputs.
	\subsubsection*{Week6}
		I finished working on the production mode and then put the finishing touches on it with Claude. I made it so the camera would take 40 frames, but discard the first 10 frames in case the camera is still warming up. Then the program averages the temperature data from all of the 30 remaining frames, and then takes the average of the 30 averages. This is then used as the output as the predicted core body temperature.

		We also cleaned up the GitHub repository this week, as well as adding readmes to all of the necessary files.
	\subsubsection*{Week7}
		This week we had expo, so everything was finished. Nothing much was done other than expo.
	\subsubsection*{Week8}
		The final report was assigned this week. I didn't do much other than write one of my sections in the final report.
	\subsubsection*{Week9}
		This week was dedicated to working on the final report. I finished up my sections and started to work on some other sections as well to get the report done faster. The document should be done soon, just need to convert into latex later and figure out how to add images/code to the latex document.

		We also need to start on our presentation soon.
	\subsubsection*{Week10}
		Finished up the final report and presentation this week. Finally done with this project as a whole.
