\subsection*{Fall}
\subsubsection*{Week1}
	This week I read through all of the project proposals and chose my top choices. 
\subsubsection*{Week2}
	This week we received our project topic. We emailed our client to introduce ourselves and set up a time to meet with him. I also worked on the problem statement assignment. 
\subsubsection*{Week3}
	I finished my individual problem statement. My group and I met with our client on Friday for the first time. We also met with our TA on Friday. 
\subsubsection*{Week4}
	This week my team and I worked on the final problem statement.  We met with our client and redefined our final solution. We understood that this is a proof of concept project and the solution might not work. We are going to test this approach and do our best to figure out if we can estimate the core body temperature from the images. 
\subsubsection*{Week5}
	This week we focused on our project's requirements. We started writing them down but we noticed that we didn’t have enough information. When we met with our client, he helped us with defining more requirements for the project. We discussed the camera the mechanical team is going to use and the tools we should use to learn how to process the images from the camera. 
\subsubsection*{Week6}
	This week we worked on our requirement  document. It was really helpful to focus on that because it gave us a better understanding on the project. Now it is clearer what the final product needs to be. We still need some more clarification from the client but overall we understand our project better now.
\subsubsection*{Week7}
	We've divided the project to three parts and each person it responsible to write on one. I will be responsible to working on the image processing part. I will need to cut the person from the image, and process the pixels out. I've been researching different technology options to do this. 
\subsubsection*{Week8}
	This week I finished the tech review document. It was helpful to look into the different technologies and learn more about image processing. It showed me that there were so many resources for image processing. 
\subsubsection*{Week9}
	This week was Thanksgiving week so I there wasn't a lot of time to get stuff done. I worked on fixing and finishing up my tech review document. I also started working on my design document draft. 
\subsubsection*{Week10}
	This week we met with Bill and Andrew to discuss some of our problems with the project. We weren't sure if we could meet the reequipments for the project in time so we had to redefine it.  
	

\subsection*{Winter}
\subsubsection*{Week1}
	First week of Winter term. We finished all of our documents from Fall term and started processing thermal images from the camera. 
\subsubsection*{Week2}
	We met with the mechanical team to talk about where we are in the project and what they've been up to. They will provide us a distance of which the camera will be positioned at. This way we will know how to take our images for now. We also decided that we need to start working on the AI part of the project.  
\subsubsection*{Week3}
	This week Brian and I worked on the image processing code. We are almost done with most of it. If you don't count the camera problems.We need to start working on the model soon. I hope that we will start working on it this weekend or at the beginning of next week. We have a lot more to do for the project. 
	
\subsubsection*{Week4}
	 We are trying to figure out how to use the camera in the right way. It gives weird temperature readings. We need to see if the difference in the temperature is always "wrong" in the same way. If not, we will have to find a better way to calibrate the camera. Other than that, we are stuck on the model part. We are waiting to hear from Andrew. 
	
\subsubsection*{Week5}
	Started working on the report and the poster. Got some progress with the camera, finally got some good readings. Met with Andrew to talk about our progress and about the model. Bill gave us some ideas for the model part. Over all we're making progress. 
\subsubsection*{Week6}
	We worked on the report and the poster this week. We need to do a lot more work on the poster. We also had our in-class workshop for expo, it helped us understand the best way to talk about our project in expo. This week was a little stressful because we had many assignments to submit. We met with Bill, he said that he will take care of the camera problem by the weekend, we haven't  heard from him yet but we hope that it will be done by Monday. 
	
\subsubsection*{Week7}
	We didn't meet with Bill this week because we didn't have anything new. We met with his graduate student, Chris who helped us with importing the images from the camera. We still need to work with them on calibrating the camera. On Friday, Brian and I took the camera and tried what Bill suggested. We had a cup of coffee on the table and we took a picture every 5 minutes. The results were bad because the temperature of the table changed when the coffee's temperature changes, this is exactly what we didn't want to happen. 
\subsubsection*{Week8}
	Brian and I met with Chris on Tuesday. We worked on the code to make the camera take an image and import it into the code and get the temperature values and enter them into a CSV. We got it to work but it returns values that are off by 3-4 Celsius . We emailed Bill about it and he said that this will work. Next we need to start collecting data. We need to go take pictures of people and take their body temperature at the same time and enter those data points into our code. 
\subsubsection*{Week9}
	This week was really busy for all of us so we didn't make much progress.
\subsubsection*{Week10}
	This week we worked on taking new images to get data for the model. Unfortunately, after taking the images, we notices that the csv values are still off. They are higher than they are supposed to be. I emailed Chris, the graduate student, to try to work on this but I don't know if we we'll get it done by the end of the term. 
	
\subsection*{Spring}

\subsubsection*{Week1}
	I worked on the image processing code to try and help with the calibration of the camera. I think the image processing is done. Brian and I met to work on the poster, we made a lot of progress on the poster. 
	
\subsubsection*{Week2}
	This week we divided the responsibilities that we have left. I am going to go over the documents and see what we need to change. Bianca will try to finish the poster. Brian will do the production mode.
\subsubsection*{Week3}
	We met with Bill this week. We talked to him about making some changes to some of our documents. He said the document changes are fine and that the poster is fine. He said there will be a graduate student that will try to collect some data for us. 
\subsubsection*{Week4}
	This week we worked on finishing the poster. We had to make many small corrections  to make it look good. We added the logos and a picture of the mechanical team structure. We also tool the team picture. I submitted the poster for printing. 
	
\subsubsection*{Week5}
	This week we met with Andrew and we talked about trying to normalize the data. He suggested an approach to normalize the data but our client didn't want us to use it because he didn't think that normalizing the data will help with the calibration problem. Our client Bill write some code for the model and gave it to us as an example of a possible model. He also gave us a list of a few different models that would be good to try on our data.  
\subsubsection*{Week6}
	This week we worked on making sure our code is ready for the code freeze. We organized the GitHub repository and worked on our production mode for Expo. 

\subsubsection*{Week7}
	We spent the week preparing for expo. We saw that we didn't get the space that we asked for so we decided to just put the camera on the table at expo. In expo there were too many people so we could run our program (it need only one person in the frame). We ended up just running the camera software and explaining people about our project. People seemed to really like it. It was fun explaining it to people, especially the kids. 
\subsubsection*{Week8}
	This week I started working on the final report for our client. We need to give him a report that will explain everything that we've done so his graduate student could continue the work. 
\subsubsection*{Week9}
	This week I worked on the report for Bill  and the final report for the class. For the final report for the class I started by putting all of the required documents together in one big LaTex file. 
\subsubsection*{Week10}
	This week we worked on finishing the report and the presentation for the class. 